%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Huidong}{Xu}{

\urlstyle{same}
Mail: \href{mailto:391678792hd@sjtu.edu.cn}{391678792hd@sjtu.edu.cn} \\ 
Tel: 19821870756 \\
GitHub: \href{https://github.com/WilliamX1}{WilliamX1}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Shanghai Jiao Tong \\ University}
\descript{MINGHANG SHANGHAI}
\location{
Major in Software Engineering \\
Cum. Scores: 88.23 / 100 \\
Cum. GPA: 3.78 / 4.3 \\
Major Scores: 88.43 / 100 \\
Major GPA: 3.79 / 4.3 \\
}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Linear Algebra \\
Curriculum design of programming \\
Introduction to computer system \\
Programming and data structures \\
Software engineering \\
Technology for web developing \\
\sectionsep

\subsection{Self Learning}
Machine learning \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
C/C++ \\
\location{Over 1000 lines:}
Python \textbullet{} Java \\
\location{Familiar:}
Matlab \textbullet{} Html5/CSS3 \textbullet{} JavaScript \textbullet{} MySQL \\
\sectionsep

\subsection{others}
\location{Skilled}
Markdown \textbullet{} MS Office \\
\location{Familiar:}
PhotoShop \textbullet{} Premiere Pro \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{PROGRAMMING}
\descript{| PROJECTS | DEVELOPED OR JOINED }
\location{Sep 2019 - Present}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item \href{https://github.com/WilliamX1/SJTU-SE/tree/main/SEP/project-snake}{\textbf{Greedy Snake Game.}} - A small game based on C++ and QT as the project in course SE127.
\item \href{https://github.com/WilliamX1/SJTU-SE/tree/main/DS/Mini-Basic-v2}{\textbf{Mini Basic.}} - A simple basic interpreter based on C++ and QT. Got close to full marks in the major course SE2322.
\item \href{https://github.com/WilliamX1/spider-dangdang}{\textbf{Crawler.}} - A Crawler that crawls nearly all data on Dangdang based on Python and Scrapy.
\item \href{https://github.com/WilliamX1/passthemon}{\textbf{PassThemOn.}} - A mobile app developed in the summer semester based on Java. Won the second highest score in the major course SE128.
\item \href{https://github.com/WilliamX1/bookstore}{\textbf{Online Bookstore.}} - A naive web app as the project in course SE2321 and SE3353.
\item \textbf{AGV Car.} - A SJTU PRP (Participation in car control), still ongoing.
\item \href{https://github.com/WilliamX1/leetcode}{\textbf{LeetCode.}} - More than 300 questions completed.
\end{tightemize}
\sectionsep

\runsubsection{STUDYING}
\descript{| MATERIALS \& ONLINE CLASS}
\location{Aug 2021 - Present}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item \href{https://www.coursera.org/learn/machine-learning}{\textbf{Machine Learning}} - A relative online class that I'm studying on.
\item \href{https://scikit-learn.org/stable/getting_started.html}{\textbf{Scikit-learn.}} - An open source machine learning library that I'm learning.
\item \href{https://ipads.se.sjtu.edu.cn/courses/cse/labs/lab1.html}{\textbf{ChFS.}} - An inode-based network file system that I'm working on.
\item \href{https://github.com/WilliamX1/RM2022-Cypher}{\textbf{RoboMaster.}} - A robot competition that I'm working on as the programmer.  
\end{tightemize}
\sectionsep

\runsubsection{DAILY}
\descript{| LEADERSHIP \& ACTIVITIES }
\location{Sep 2019 - Present}
\begin{tightemize}
\item \textbf{Monitor} of the class F1903703.
\item \textbf{Member} of the debate team in SEIEE (School of Electronic Information and Electrical Engineering).
\item \textbf{Programmer} of Champions League on VEX Robot School Competition.
\item \textbf{Member} of the 129 Gala Champions League in 2020.
\item \textbf{Host} of the Welcome Party of Software Engineering.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2020         & University  & Merit Student\\
2020         & University  & Excellent League Member\\
2020	     & University  & Chandler-Chi Family Scholarship\\
2020	     & University  & B-level School Scholarship\\
2021	     & University  & Electric Academy Heritage Fund Scholarship\\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
