% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Huidong Xu}

\basicInfo{
  \email{HuiD\_Xu@163.com} \textperiodcentered\ 
  \phone{(+86) 19821870756} \textperiodcentered\ 
  \github[WilliamX1]{https://github.com/WilliamX1}
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Shanghai Jiao Tong University (SJTU)}, Shanghai, China}{Sep. 2019 -- Present}
\textit{B.S.} in Software Engineering (SE), expected June 2023 \\
Major Scores: 88.43 / 100, Major GPA: 3.79 / 4.3

\section{\faUsers\ Programming \& Studying}
\datedsubsection{\href{https://github.com/WilliamX1/SJTU-SE/tree/main/SEP/project-snake}{\textbf{Greedy Snake Game}}}{Sep. 2020 - Jan. 2021}
A small game based on C++ and QT as the project in course SE127.
\datedsubsection{\href{https://github.com/WilliamX1/SJTU-SE/tree/main/DS/Mini-Basic-v2}{\textbf{Mini Basic}}}{Mar. 2021 - Jun. 2021}
A naive basic interpreter based on C++ and QT with complementing LSM tree. Got close to full marks(98/100) in the major course SE2322.
\datedsubsection{\href{https://github.com/WilliamX1/spider-dangdang}{\textbf{Crawler}}}{Aug. 2021}
A crawler that crawls nearly all data on Dangdang based on Python and Scrapy.
\datedsubsection{\href{https://github.com/WilliamX1/passthemon}{\textbf{PassThemOn}}}{Jul. 2021 - Sep. 2021}
A mobile app developed in the summer semester based on Java. Won the second highest score in the major course SE128.
\datedsubsection{\href{https://github.com/WilliamX1/bookstore}{\textbf{Online Bookstore}}}{Mar. 2021 - present}
A naive web app as the project in course SE2321 and SE3353.
\datedsubsection{\textbf{AGV Car}}{Sep. 2021 - present}
A SJTU PRP(Participation in car control), still ongoing.
\datedsubsection{\href{https://github.com/WilliamX1/leetcode}{\textbf{LeetCode}}}{Apr. 2021 - present}
More than 300 questions completed.
% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C/C++ > Python > Java == Matlab
  \item Platforms: Windows / MacOS / Linux
  \item Tools: Markdown / MS Office
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\begin{itemize}
    \item \datedline{ Merit Student }{May. 2020}
    \item \datedline{ Excellent League Member }{May. 2020}
    \item \datedline{ Chandler-Chi Family Scholarship}{Sep. 2020}
    \item \datedline{ B-level School Scholarship}{Sep. 2020}
    \item \datedline{ Electric Academy Heritage Fund Scholarship}{Apr. 2021}
\end{itemize}


\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: https://github.com/WilliamX1
  \item Languages: English - Fluent, Chinese - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
